%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{comment}
\usepackage{fontawesome}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\renewcommand{\labelitemi}{--} % Changes the first-level bullet to a dash
% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item[--]\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Aneesh Iyer} \\ \vspace{1pt}
    \small \faPhone\ (513) 399-1607 $|$ \href{mailto:aiyer@gatech.edu}{\underline{\faEnvelope\ aiyer@gatech.edu}} $|$ 
    \href{https://linkedin.com/in/aneesh-iyer}{\underline{\faLinkedin\ in/aneesh-iyer}} $|$
    \href{https://github.com/aneesh-iyer29}{\underline{\faGithub\ github.com/aneesh-iyer29}} $|$ \href{https://aneesh-iyer.com/}{\underline{\faGlobe\ aneesh-iyer.com}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{May 2028}
      {B.S. in Computer Engineering --- Cybersecurity \& Systems/Architecture --- GPA: 4.0}{Atlanta, GA}
      \begin{itemize}[label=--]
          \item Relevant Coursework: Data Structures \& Algorithms, Hardware/Software Systems Programming \\In Progress: Computer Architecture, Cryptographic Hardware for Embedded Systems
      \end{itemize}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Transpira Labs (Backed by Christopher Klaus)}{May 2026 -- Present}
      {Software Engineer}{Atlanta, GA}
      \resumeItemListStart
        \resumeItem{Developed full-stack services for a platform to support 40+ expert contractors building frontier AI training data.}
        \resumeItem{Packaged 288 supply-chain benchmark tasks into a reproducible environment with deterministic rewards.}
        \resumeItem{Created a benchmark for LLM agents on their ability to RL train agents, revealing under 1\% lift from instruction.}
    \resumeItemListEnd
    \resumeSubheading
      {Nuntius (YC S'25)}{Sep. 2025 -- Apr. 2026}
      {Software Engineer}{Remote}
      \resumeItemListStart
        \resumeItem{Directed a team of 8 engineers to deliver a \$50K client project for evaluating LLM agent tool-use limitations.}
        \resumeItem{Built 5+ RL environments with automated graders and custom rewards; created 300+ adversarial tasks.}
        \resumeItem{Designed trajectory-aware evaluators assigning partial credit based on intermediate steps instead of binary results.}
    \resumeItemListEnd

    \resumeSubheading
      {\href{https://github.com/Avionics-Propulsion-Landers-GT/MonopropUAV}{\underline{GT Propulsive Landers}}}{Jan. 2026 -- Present}
      {Guidance, Navigation, and Control Team Member | Python, Rust}{Atlanta, GA}
      \resumeItemListStart
        \resumeItem{Automated PID tuning for a 1.8 kN engine simulation via 8 step-response metrics logged to CSV each run.}
        \resumeItem{Engineered sensor fusion pipelines with 3 distinct EKFs spanning IMU, GPS, and LIDAR to filter noisy inputs.}
        \resumeItem{Achieved a 0.63\% average deviation from simulated ground-truth, demonstrating robust estimation accuracy.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{\href{https://build.transpiralabs.com}{\underline{Build: Scratch for RL Environments}}} $|$ \emph{Python, TypeScript, HUD}}{Jun. 2026}
          \resumeItemListStart
            \resumeItem{Won 1st of 70 (\$50K+ in prizes/credits) at the HUD $\times$ Y Combinator Frontier/RSI RL Environments Hackathon.}
            \resumeItem{Developed an open-source Scratch-style platform compiling plain-language block trees into RL environments.}
            \resumeItem{Enabled anyone to evaluate models in custom simulations and launch RL training runs without writing any code.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{\href{https://doi.org/10.1137/25S1777554}{\underline{Mathworks Math Modeling (M3) Champion}}} $|$ \emph{Python, R}}{Mar. 2025 -- May 2025}
          \resumeItemListStart
            \resumeItem{Modeled Memphis heat resilience and electricity demand, winning 1st of 794 teams (\$20,000 grand prize).}
            \resumeItem{Quantified vulnerability across 27 zip codes by reducing variables to 4 significant features via backward selection.}
            \resumeItem{Presented findings to Ph.D. professors and co-authored a publication in SIAM Undergraduate Research Online.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------LEADERSHIP & VOLUNTEERING-----------
\section{Volunteering}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Science Olympiad National Team} $|$ \emph{TypeScript, Web Development}}{Aug. 2025 -- Present}
          \resumeItemListStart
            \resumeItem{\href{https://github.com/toebes/ciphers}{\underline{Open-source maintainer}} for the Codebusters \href{https://toebes.com/codebusters/}{\underline{platform}} used by 1,000+ coaches/volunteers nationwide.}
            \resumeItem{Volunteered and supported exam administration for 2,000+ students at state and national level tournaments.}
            \resumeItem{Member of the GT Alumni Chapter, organizing exam logistics for 40 teams at the GA State Tournament.}
          \resumeItemListEnd
      \resumeProjectHeading{\textbf{ScioVirtual Foundation Volunteer} $|$ \emph{HTML, CSS, JS}}{Summers 2024 -- 2026}
      \resumeItemListStart
        \resumeItem{Volunteered 100+ hours teaching STEM courses to kids aged 11-14 for the ScioVirtual NonProfit Foundation.}
        \resumeItem{Created a cryptography training platform for 70+ students with feedback and automated solution verification.}
        \resumeItem{Achieved the highest-rated course by students among 20+ offerings and was named 2025 Instructor of the Year.}
\resumeItemListEnd
\resumeSubHeadingListEnd
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, Rust, C, TypeScript/JavaScript, SQL, R, MATLAB, HTML/CSS, Bash, \LaTeX} \\
     \textbf{AI/ML}{: RL Environment Creation, LLM Evaluation \& Benchmarking, RLVR/GRPO, NVIDIA NeMo Gym} \\
     \textbf{Tools \& Systems}{: Docker, Git, Pydantic, Arduino, RISC-V, Control Systems, Sensor Fusion, Embedded Systems} \\
     \textbf{Interests}{: Machine Learning, Cryptography, Cybersecurity, Aerospace Systems, Optics, Spanish (Intermediate)}
    }}
 \end{itemize}

 
%-------------------------------------------
\end{document}